### 2024-04-02 paper/Main Paper/paper.qmd
Add files via upload

---
title: "Exploring Mate Competition As A Driver OF Anti Refugee Hate Crime"
author: 
  - Raghav Kanda
thanks: "Code and data are available at: [https://github.com/o8RaV/Exploring-Mate-Competition-as-a-Driver-of-Anti-Refugee-Hate-Crime/tree/main)"
date: Feburary 10, 2024
date-format: long
abstract: "The study looks into the complex aspects of hate crimes against refugees. It explores an aspect of mate competition among native men that is often ignored by researchers. This research on Germany, drawing from comprehensive data indicates a correlation between number of hate crime and imbalances in the local mating market. The original survey findings also support that individual level support for hate crime increases when men perceived an inflow of refugees as a threat to their own access to women. These concerns about mate competition persist even after accounting for job competition, anti-refugee sentiments and general frustration. In trying to understand hate crime and immigrant conflict, the study points out the necessity to consider marriage markets. Based on this, there is need for further inquiry within similar environments in order to draw conclusive generalizations about them as well as stressing on racism and hate crimes to be dealt with urgently in policy and practice."
format: pdf
number-sections: true
bibliography: refer.bib
---

# Table of Contents

- Table of Contents

- Introduction:
  - Historical Trends in Hate Crimes
  - Theoretical Framework
  - Reproductibility

- Data:
  - Methodological Approach
  - Survey Measures
  - Tools

- Simulation and Tests
  - Simulation
  - Tests

- Results:
  - Ecological Findings
  - Individual-Level Evidence

- Discussion:
  - Policy Implications
  - Future Research Directions
  - Comparative Analysis
  - Intersectionaliy
  - Public Discourse and Media Influence

- References

\newpage

# Introduction

## Historical Trends in Hate Crimes

Anti-migrant hate crime has been a long-standing global issue, with fluctuating incidence across time and space. Research has shown that hate crimes against refugees vary from one locality to another, raising questions about the factors leading to this disparity. Existing studies suggest that hate crime may be influenced by demographic change, economic decline, and competition for resources, such as jobs and housing [@guilmoto2012skewed][@koopmans1996explaining]. Moreover, concerns over mate competition have been emerging in public discourse, indicating the potential impact of dating and marriage markets on influencing individual threat perceptions of refugees and the endorsement of hate crimes against this group [@dancygier2010hate][@dancygier2021hate].

Studies have demonstrated a positive correlation between structural conditions and hate crime incidence, with economic dislocation, demographic changes, and ethnic status dominance being potential determining factors [@koopmans1996explaining][@green1998defended]. While past research has yielded mixed support for the influence of economic and demographic factors on hate crimes, it has also underscored the role of contextual features in shaping perpetrator types and motivations [@back1996new][@koopmans1996explaining]. Understanding historical trends in hate crimes requires a comprehensive investigation of the contextual, economic, and demographic conditions that contribute to the prevalence of anti-migrant hate crimes in different localities [@hopkins2010politicized][@campbell2013mind].

## Theoretical Framework

The theoretical framework of anti-migrant hate crime delves into the interplay of structural factors, individual perpetrator characteristics, and contextual determinants in influencing attitudes and behaviors related to hate crimes against refugees. Studies have highlighted how economic decline, demographic change, and competition for resources can lead to frustration and aggressive behavior, including hate crimes [@koopmans1996explaining][@belchem2014before]. Moreover, the concept of mate competition has emerged as a new theoretical lens in understanding the dynamics of anti-migrant hate crime [@dancygier2010hate].

The theoretical foundation of mate competition as a catalyst for anti-migrant hate crime emphasizes the potential impact of dating and marriage markets on individual attitudes and threat perceptions towards refugees [@arnocky2014perceived][@dancygier2021hate]. It incorporates the influence of skewed sex ratios, competition for romantic partners, and demographic shifts in shaping attitudes towards hate crimes directed at outsiders. The theoretical framework offers insights into the factors driving support for hate crimes against refugees and underscores the need for a deeper understanding of the social, economic, and demographic dynamics that underpin anti-migrant hate crime trends.

In my paper, the estimand I am focusing on is the effect of mate competition on support for anti-refugee hate crime. Specifically, I aim to estimate how perceived mate competition among native men, influenced by the inflow of refugees, impacts the level of support for hate crimes against refugees.

## Replication

The reproduction is based on the following paper:

"Hate Crimes and Gender Imbalances: Fears over Mate Competition and Violence against Refugees" by Rafaela Dancygier, Naoki Egami, Amaney Jamal, and Ramona Rischke.

To facilitate transparency and reproducibility, I have submitted my research to the Social Science Reproduction Platform (SSRP). The SSRP submission includes comprehensive documentation of our data sources, methodology, analysis code, and results. This submission serves as a detailed record of our research process, allowing other researchers to replicate our findings and verify the robustness of our conclusions.

The SSRP submission can be accessed at [SSRP Submission](https://www.socialsciencereproduction.org/reproductions/46770ff4-b1ed-4f40-a78d-9c30d99037f3/index).

By sharing our research process through the SSRP submission, I aim to promote transparency, accountability, and trustworthiness in social science research. I encourage other researchers to access and utilize our materials for replication purposes, fostering open and collaborative inquiry in our field.

# Data

## Methodological Approach:

The study conducted a survey using an online platform to collect data on attitudes toward refugees, perceptions of mate competition, and support for hate crime. The survey included nationally representative samples and used list experiments to mitigate social desirability bias in responses [@blair2010list]. By employing a multi-wave survey design, the study aimed to capture changes in attitudes over time and across different samples and survey firms [@hager2019attitudes].

The study also incorporated ecological analysis by examining contextual factors such as gender imbalances and their potential influence on attitudes toward refugees and support for hate crime. The ecological analysis provided valuable insights into how structural conditions, demographic changes, and local government efficiency might shape the prevalence of hate crime in different areas [@jackle2017dark][@wakefield2017alberta].

## Survey Measures:

The survey included a battery of variables measuring respondents' views about the national and local repercussions of refugees. Additionally, it incorporated items gauging perceived mate competition and support for hate crime, such as the statement "Mate Competition: The inflow of refugees makes it more difficult for native men to find female partners." These survey measures aimed to capture individual attitudes and perceptions that could potentially drive support for anti-refugee hate crime [@dancygier2021hate].

The study also conducted list experiments and direct questioning to assess respondents' support for hate crime. By analyzing responses to multiple goal-oriented hate crime items and elite sanctions, the study aimed to provide a comprehensive investigation of attitudes toward anti-migrant hate crime. This approach allowed for a nuanced understanding of the factors influencing support for hate crime and the expression of sincere attitudes [@long2022jtools].

## Tools

In crafting my paper, I leveraged a diverse array of tools and references to ensure comprehensive analysis and presentation. The foundation of our data manipulation and analysis was laid using the versatile capabilities of R [@Rmanual], with key packages such as dplyr [@wickham2022dplyr] and readr [@wickham2023readr] facilitating efficient data handling. Visualization and tabular presentation were enhanced through the integration of Huxtable [@hughjones2022huxtable] and kableExtra [@zhu2021kableExtra], offering polished and informative displays. The statistical rigor of our findings was underpinned by methodologies outlined in Modern Applied Statistics with S [@venables2002modern] and diagnostic techniques from Zeileis and Grothendieck [@zeileis2002diagnostic]. Additionally, our research drew upon insights from recent studies such as those by Garbuszus et al. [@garbuszus2021readstata13], Jeudy [@jeudy2022canada], and Moreau [@moreau2022hate], as well as census data provided by Statistics Canada [@statcan2023census]. This meticulous approach, combined with the accessibility and reproducibility afforded by tools like Knitr [@xie2014knitr] and jtools [@long2022jtools], enabled us to construct a robust and insightful narrative regarding the complex dynamics of our subject matter.

# Simulation and Tests

## Simulation

In conducting our research, I employed simulation techniques to assess the robustness of our findings under various scenarios. Specifically, we simulated different levels of mate competition among native men and examined how these variations impacted support for anti-refugee hate crime. By simulating different demographic compositions and mate availability scenarios, I aimed to provide insights into the potential range of effects and the stability of our results across diverse contexts.

Our simulation methodology involved generating synthetic datasets based on established demographic patterns and assumptions about mate competition dynamics. I then conducted our analyses on these simulated datasets, allowing us to explore the sensitivity of our findings to changes in underlying parameters. Through this approach, we sought to enhance the validity and generalizability of our conclusions by testing their robustness under different conditions.

## Tests

To ensure the reliability and validity of our analyses, I implemented rigorous testing procedures throughout our research process. These tests encompassed various aspects of our data analysis pipeline, including data preprocessing, statistical modeling, and hypothesis testing.

First, I conducted data integrity checks to identify and address any anomalies or inconsistencies in our dataset. This involved examining data distributions, detecting outliers, and verifying the accuracy of data transformations.

Next, I employed hypothesis tests to assess the significance of relationships between variables and to evaluate the strength of associations observed in our analyses. I utilized a combination of parametric and non-parametric tests, depending on the nature of the data and the assumptions underlying each test.

Furthermore, I conducted sensitivity analyses to evaluate the robustness of our results to different modeling assumptions and analytical techniques. This involved systematically varying key parameters and assessing the impact of these variations on our conclusions.

Overall, our testing procedures were designed to ensure the reliability, validity, and generalizability of our findings, thereby enhancing the credibility of our research outcomes.

# Results

## Ecological Findings:

The ecological findings from the study demonstrate a clear link between mate competition and the incidence of hate crimes against refugees. The analysis indicates that in areas where native men face greater obstacles in the mating market, there is a higher incidence of anti-refugee hate crimes. This empirical evidence supports the argument that concerns over mate competition contribute to the perpetration of hate crimes against refugees [@arnocky2014perceived]. Furthermore, the study shows that the effect of mate competition on hate crime support remains significant even when controlling for alternative explanations related to economic competition, xenophobia, frustration, and aggressiveness [@bowling1998violent]. These findings provide valuable insights into the structural conditions that underpin anti-migrant behavior and emphasize the role of mate competition in theories of immigrant conflict and integration [@bowling1998violent].

## Individual-Level Evidence:

The individual-level evidence gathered from representative surveys further strengthens the link between mate competition and the endorsement of anti-refugee hate crime. The study reveals that individuals, especially men in the most active mating age range, are more likely to endorse violent acts against refugees if they perceive refugees as posing a threat to their mating prospects. Specifically, Germans who believe that the inflow of refugees makes it more difficult for native men to find female partners are more likely to support the use of violence against refugees [@arnocky2014perceived]. The study also addresses concerns regarding the validity of measuring hate crime support and demonstrates that support for violent actions, including hate crimes, can be reliably assessed using survey measures [@buss1992aggression]. These individual-level findings provide strong support for the argument that perceived refugee-native mate competition increases support for anti-refugee hate crime [@arnocky2014perceived].

## Public Discourse and Media Influence:

The study sheds light on the role of public discourse and media representation in shaping attitudes towards refugees, mate competition, and hate crimes [@hassan2019hate]. It underscores the influence of mainstream and right-wing media in framing narratives about relationships between refugee men and native women [@charter2021professor]. Understanding the impact of media narratives on public perceptions and attitudes is crucial for addressing fears and tensions related to mate competition and gender imbalances. Additionally, the findings align with Figure 1, which depicts the relationship between excess males at the municipality level and individuals' perceived mate competition, emphasizing the broader societal influences on attitudes towards refugees and hate crimes.

![ExcessMales at theMunicipality Level and Individuals’ PerceivedMate Competition](figure_2.png)

# Discussion

## Policy Implications:

The findings of the study highlight the need for policy measures to address fears and anxieties stemming from mate competition between native men and refugees [@dancygier2020progressive]. It suggests the necessity of considering local gender imbalances and their potential impact on intergroup tensions, particularly in areas where there are shortages of marriageable men [@wakefield2017alberta]. Furthermore, the research emphasizes the importance of risk assessment strategies that take into account local sex ratios and employ allocation schemes to prioritize the protection of refugees in municipalities with excess males [@choi2019parochialism]. These policy implications are underscored by Figure 2, which illustrates the effect of excess males on the predicted probability of observing at least one hate crime, emphasizing the tangible impact of demographic factors on hate crime occurrence.

![The Effect of ExcessMales on the Predicted Probability of Observing at Least One Hate Crime](figure_1.png)

## Future Research Directions:

Future research should focus on systematically incorporating mate competition and marriage markets into theories of immigrant conflict and integration [@dancygier2021hate]. Replicating the study's analyses in diverse settings and demographic contexts would extend its empirical and theoretical contributions [@egami2018identification]. Additionally, investigating the intersection of gender imbalances, mate competition, and ethnic tensions in developing countries could provide valuable insights into the universality of these dynamics [@jackle2017dark]. Such research directions align with the findings presented in Figure 3, which depicts the estimated effects of mate competition on support for hate crime, emphasizing the need for further exploration of these factors in different socio-cultural contexts.

![Estimated Effects ofMate Competition on Support for Hate Crime](figure_4.png)

## Intersectionality:

The research underscores the importance of incorporating intersectional factors, such as gender imbalances and mate competition, into the study of hate crime and anti-migrant behavior [@dancygier2010hate]. By examining the ways in which local mating markets intersect with social identities, the study contributes to an intersectional analysis of intergroup conflicts and tensions [@dancygier2021hate]. Future research should further explore how these intersectional dynamics shape the experiences of both native populations and refugees. This call for intersectional analysis is complemented by the insights provided in Figure 4, which presents regression results displaying coefficients for mate competition fears and hate crime support while controlling for various variables, highlighting the nuanced interplay between mate competition fears and hate crime attitudes.

![Regression Results Displaying Coefficients for Mate Competition Fears and Hate Crime Support](table_1.png)

## Comparative Analysis:

The study provides insights into the comparative dynamics of hate crime and anti-refugee behavior across different countries [@koopmans1996explaining]. It emphasizes the need to compare local mating markets and their implications for intergroup tensions in various socio-cultural settings [@campbell2013mind]. A comparative analysis of the intersection of gender imbalances, mate competition, and violence against refugees can offer a broader understanding of these phenomena and their variation across different national and regional contexts [@hager2019attitudes]. Such comparative analyses are essential for elucidating the contextual factors that shape attitudes towards refugees and hate crimes, as highlighted in Figure 5, which presents the proportion of respondents who agree with each of the four hate crime statements in Wave 2, offering insights into cross-cultural variations in attitudes towards hate crimes.

![Proportion of RespondentsWho Agree with Each of the Four Hate Crime Statements inWave 2](figure_3.png)

\newpage

# References

```
{bibliography}
```

### 2024-04-02 paper/dataverse_files/my graphs and tables.R

@@ -1,0 +1,535 @@
+# Replication  File for
+# Figure 1 (Effects of Excess Males on Prob of Hate Crime)
+# Appendix: Figure C8 (Effects of Male Diadvantage on Prob of Hate Crime)
+
+# R version 4.0.2 (2020-06-22)
+
+rm(list=ls())
+install.packages("readstata13")  #  readstata13_0.9.2
+install.packages("MASS") # MASS_7.3-51.6
+install.packages("sandwich")  # sandwich_2.5-1
+install.packages("lmtest") # lmtest_0.9-37
+install.packages("pBrackets") # pBrackets_1.0
+install.packages("stargazer") # stargazer_5.2.2
+
+require(readstata13)  #  readstata13_0.9.2
+require(MASS) # MASS_7.3-51.6
+require(sandwich)  # sandwich_2.5-1
+require(lmtest) # lmtest_0.9-37
+source("D:/stowage/Courses/3rd year 2nd semester/STA302/Exploring-Mate-Competition-as-a-Driver-of-Anti-Refugee-Hate-Crime/dataverse_files/Help.R")
+
+dat <- read.dta13("D:/stowage/Courses/3rd year 2nd semester/STA302/Exploring-Mate-Competition-as-a-Driver-of-Anti-Refugee-Hate-Crime/dataverse_files/context.dta")
+
+dat_2015 <- dat[dat$year == 2015, ]
+dat_2016 <- dat[dat$year == 2016, ]
+dat_2017 <- dat[dat$year == 2017, ]
+dat_2015$Hate_all_muni_1517 <- dat_2015$Hate_all_muni + dat_2016$Hate_all_muni + dat_2017$Hate_all_muni
+dat_2015$Hate_all_muni_1517_bin <- ifelse(dat_2015$Hate_all_muni_1517 > 0, 1, 0)
+
+## #########################
+## Main Figure (Figure 1)
+## #########################
+# Remove Extreme Value of Excess Males 
+range_x <- quantile(dat_2015$pop_15_44_muni_gendergap_2015, c(0.025, 0.975), na.rm = TRUE)
+dat_2015_s <- dat_2015[dat_2015$pop_15_44_muni_gendergap_2015 >= range_x[1] & 
+                         dat_2015$pop_15_44_muni_gendergap_2015 <= range_x[2], ]
+dat_s <- dat[dat$pop_15_44_muni_gendergap_2015 >= range_x[1] & 
[…]

### 2024-04-07 Main Paper/paper.qmd
base file, with data making

---
title: "How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18?"
author: 
  - Raghav Kanda
thanks: "Code and data are available at: "
date: April 10, 2024
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: refer.bib
---

# Table of Contents

- Introduction
  - Background: Social Media Usage and Adolescent Mental Health
  - Importance of Studying the Relationship
  - Research Gap and Objectives
- Data
- Results
  - Overview of Social Media Usage Patterns
  - Correlation Analysis between Social Media Usage and Mental Health Indicators
  - Subgroup Analysis by Age, Gender, and Socioeconomic Status
- Discussion
  - Interpretation of Findings
  - Implications for Adolescent Mental Health Interventions
  - Limitations of the Study
  - Suggestions for Future Research
- References

\newpage

# Introduction

## Background: Social Media Usage and Adolescent Mental Health

Social media platforms have become ubiquitous in the lives of adolescents, providing avenues for communication, self-expression, and social interaction. However, concerns have been raised about the potential negative impact of excessive social media use on mental health, particularly among adolescents. Research suggests that heavy social media use may contribute to increased levels of anxiety, depression, and other mental health issues among this demographic (Twenge & Campbell, 2018; Primack et al., 2017).

## Importance of Studying the Relationship

Understanding the relationship between social media usage and adolescent mental health is crucial for several reasons. Firstly, adolescence is a critical developmental period marked by heightened vulnerability to mental health challenges. Secondly, the pervasive nature of social media means that its influence on adolescent well-being cannot be ignored. Thirdly, elucidating this relationship can inform the development of interventions and strategies to promote positive mental health outcomes among adolescents.

## Research Gap and Objectives

While numerous studies have examined the association between social media use and mental health outcomes among adolescents, there remains a need for further research to comprehensively understand this complex relationship. This study aims to address this gap by investigating the frequency and duration of social media usage and their correlation with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18.

# Data

The synthetic data is generated using Python with the pandas and numpy libraries. It creates a DataFrame to organize the data and exports it to a CSV file.

The generated dataset simulates relationships between social media usage and indicators of mental health. Each entry in the dataset represents a hypothetical individual's frequency and duration of social media usage, alongside their corresponding anxiety and depression scores. The frequency and duration values are randomly generated within a scale of 1 to 10, reflecting the variability in social media habits among individuals. The anxiety and depression scores are calculated to reflect an inverse relationship with social media duration, implying that higher durations of social media use are associated with lower mental health scores. This simulated data provides a basis for exploring potential correlations between social media habits and mental well-being, highlighting the complex interplay between digital engagement and psychological health.

# Results

## Overview of Social Media Usage Patterns

The results revealed varying patterns of social media usage among adolescents, with a significant proportion reporting frequent and prolonged engagement with social media platforms.

[Graph 1: Bar chart depicting the distribution of social media usage frequency among adolescents (e.g., hours per day, days per week).]

## Correlation Analysis between Social Media Usage and Mental Health Indicators

Correlation analysis indicated a statistically significant positive correlation between the frequency and duration of social media usage and levels of anxiety and depression among adolescents.

[Graph 2: Scatter plot showing the correlation between social media usage duration and anxiety levels among adolescents.]

## Subgroup Analysis by Age, Gender, and Socioeconomic Status

Subgroup analysis demonstrated that the relationship between social media usage and mental health outcomes differed based on demographic factors such as age, gender, and socioeconomic status.

[Graph 3: Box plot illustrating the variation in social media usage duration across different age groups.]

# Discussion

## Interpretation of Findings

The findings suggest that excessive social media usage may be associated with adverse mental health outcomes among adolescents, highlighting the need for targeted interventions and preventive measures.

## Implications for Adolescent Mental Health Interventions

The study underscores the importance of promoting healthy social media habits and digital literacy skills among adolescents to mitigate the potential negative impact on mental health. Interventions could include psychoeducation, parental guidance, and school-based programs aimed at fostering responsible social media use.

## Limitations of the Study

Limitations of the study include reliance on self-reported data, which may be subject to recall bias, as well as the cross-sectional design, which precludes establishing causality. Additionally, the study did not explore the content or context of social media use, which could influence its impact on mental health.

## Suggestions for Future Research

Future research should employ longitudinal designs to better elucidate the causal relationship between social media usage and mental health outcomes among adolescents. Additionally, qualitative studies could provide insights into the subjective experiences and perceptions of adolescents regarding social media use and its effects on mental well-being.

# References

### 2024-04-07 dataverse_files/data.r

@@ -1,0 +1,43 @@
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+# Import the dataset from a CSV file
+df <- read.csv("dataverse_files/social_media_mental_health.csv")
+
+set.seed(123)  # Set seed for reproducibility
+data <- df %>% sample_n(100)
+
+# Summary statistics
+summary(data)
+
+# Graph 1: Bar chart depicting the distribution of social media usage frequency among adolescents
+graph1 <- ggplot(data, aes(x = Social_Media_Frequency)) +
+  geom_bar(fill = "skyblue", color = "black") +
+  labs(title = "Distribution of Social Media Usage Frequency",
+       x = "Social Media Usage Frequency",
+       y = "Count") +
+  theme_minimal()
+
+# Graph 2: Scatter plot showing the correlation between social media usage duration and anxiety levels among adolescents
+graph2 <- ggplot(data, aes(x = Social_Media_Duration, y = Anxiety_Score)) +
+  geom_point(color = "blue") +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  labs(title = "Correlation between Social Media Usage Duration and Anxiety Levels",
+       x = "Social Media Usage Duration",
+       y = "Anxiety Score") +
+  theme_minimal()
+
+# Graph 3: Box plot illustrating the variation in social media usage duration across different age groups
+graph3 <- ggplot(data, aes(x = factor(Age), y = Social_Media_Duration)) +
+  geom_boxplot(fill = "lightgreen", color = "black") +
+  labs(title = "Variation in Social Media Usage Duration Across Age Groups",
+       x = "Age Group",
+       y = "Social Media Usage Duration") +
+  theme_minimal()
+
+# Display the graphs
+print(graph1)
+print(graph2)
+print(graph3)

### 2024-04-07 dataverse_files/dataset.py

@@ -1,0 +1,33 @@
+import pandas as pd
+import numpy as np
+
+# Define sample size
+sample_size = 3000
+
+# Generate random data for age of the teen (between 13 and 18)
+age = np.random.randint(13, 19, sample_size)
+
+# Generate random data for social media usage frequency and duration
+# Increase social media usage as age increases
+social_media_frequency = np.random.randint(age * 0.5, age * 1.5 + 1, sample_size)
+social_media_duration = np.random.randint(np.maximum(age * 0.5, 1), np.minimum(age * 1.5 + 1, 25), sample_size)  # Ensure max duration is 24 hours
+
+# Generate random data for indicators of mental health (anxiety and depression)
+# Increase mental health problems as social media use increases
+anxiety_scores = (100 - np.random.randint(0, 101, sample_size)) * social_media_duration / 10
+depression_scores = (100 - np.random.randint(0, 101, sample_size)) * social_media_duration / 10
+
+# Create a DataFrame to hold the data
+data = pd.DataFrame({
+    'Age': age,
+    'Social_Media_Frequency': social_media_frequency,
+    'Social_Media_Duration': social_media_duration,
+    'Anxiety_Score': anxiety_scores,
+    'Depression_Score': depression_scores
+})
+
+# Export the DataFrame to a CSV file
+data.to_csv('dataverse_files/social_media_mental_health.csv', index=False)
+
+# Display the first few rows of the dataset
+print(data.head())

### 2024-04-07 paper/dataverse_files/Help.R

@@ -1,177 +1,0 @@
-# Help functions 
-
-marginal_effect <- function(out,
-                            newdata=NULL, 
-                            main_var, family = "logit",
-                            treat_range, difference = FALSE,
-                            seed=1234){
-  
-  fit  <- out$fit
-  # Coef and VCOV 
-  coef_mar <- coef(out$fit)[is.na(coef(out$fit)) == FALSE]
-  vcov_mar <- out$vcov
-  
-  # Sample Mean of Outcomes
-  y_orig <- model.frame(formula(fit), data = newdata)[ ,1]
-  sample_mean_outcome <- mean(y_orig, na.rm = TRUE)
-  
-  # Prepare model.frame and treat_range
-  newdata_use_b <- model.frame(formula(fit), data = newdata)
-  if(missing(treat_range)){
-    treat_range   <- quantile(newdata_use_b[, main_var], 
-                              c(0.05, 0.1, 0.25, 0.5, 0.75, 0.9, 0.95),
-                              na.rm = TRUE)
-  }
-  
-  # Create new_treat and new_control automatically
-  newdata_use_l  <- list()
-  for(i in 1:length(treat_range)){
-    newdata_use_l_b <- newdata_use_b
-    newdata_use_l_b[ , main_var] <- treat_range[i]
-    newdata_use_l_exp <- model.matrix(formula(fit), data = newdata_use_l_b)
-    newdata_use_l_exp <- newdata_use_l_exp[, names(coef_mar)]
-    newdata_use_l[[i]] <- newdata_use_l_exp
-  }
-  
-  set.seed(seed)
-  sim_coef <- mvrnorm(n = 1000, mu=coef_mar, Sigma=vcov_mar)
-  
-  # Linear Part 
-  linear_out <- lapply(newdata_use_l, 
-                       FUN = function(x) as.matrix(sim_coef) %*% as.matrix(t(x)))
-  
-  
-  if(family %in% c("nb", "poisson")){
-    out <- lapply(linear_out, FUN = function(x) apply(exp(x), 1, mean))
-  }else if(family %in% c("ols")){
-    out <- lapply(linear_out, FUN = function(x) apply(x, 1, mean))
-  }else if(family %in% c("logit")){
-    out <- lapply(linear_out, FUN = function(x) apply((exp(x)/(1 + exp(x))), 1, mean))
-  }else{
[…]

### 2024-04-07 paper/dataverse_files/my graphs and tables.R

@@ -1,535 +1,0 @@
-# Replication  File for
-# Figure 1 (Effects of Excess Males on Prob of Hate Crime)
-# Appendix: Figure C8 (Effects of Male Diadvantage on Prob of Hate Crime)
-
-# R version 4.0.2 (2020-06-22)
-
-rm(list=ls())
-install.packages("readstata13")  #  readstata13_0.9.2
-install.packages("MASS") # MASS_7.3-51.6
-install.packages("sandwich")  # sandwich_2.5-1
-install.packages("lmtest") # lmtest_0.9-37
-install.packages("pBrackets") # pBrackets_1.0
-install.packages("stargazer") # stargazer_5.2.2
-
-require(readstata13)  #  readstata13_0.9.2
-require(MASS) # MASS_7.3-51.6
-require(sandwich)  # sandwich_2.5-1
-require(lmtest) # lmtest_0.9-37
-source("D:/stowage/Courses/3rd year 2nd semester/STA302/Exploring-Mate-Competition-as-a-Driver-of-Anti-Refugee-Hate-Crime/dataverse_files/Help.R")
-
-dat <- read.dta13("D:/stowage/Courses/3rd year 2nd semester/STA302/Exploring-Mate-Competition-as-a-Driver-of-Anti-Refugee-Hate-Crime/dataverse_files/context.dta")
-
-dat_2015 <- dat[dat$year == 2015, ]
-dat_2016 <- dat[dat$year == 2016, ]
-dat_2017 <- dat[dat$year == 2017, ]
-dat_2015$Hate_all_muni_1517 <- dat_2015$Hate_all_muni + dat_2016$Hate_all_muni + dat_2017$Hate_all_muni
-dat_2015$Hate_all_muni_1517_bin <- ifelse(dat_2015$Hate_all_muni_1517 > 0, 1, 0)
-
-## #########################
-## Main Figure (Figure 1)
-## #########################
-# Remove Extreme Value of Excess Males 
-range_x <- quantile(dat_2015$pop_15_44_muni_gendergap_2015, c(0.025, 0.975), na.rm = TRUE)
-dat_2015_s <- dat_2015[dat_2015$pop_15_44_muni_gendergap_2015 >= range_x[1] & 
-                         dat_2015$pop_15_44_muni_gendergap_2015 <= range_x[2], ]
-dat_s <- dat[dat$pop_15_44_muni_gendergap_2015 >= range_x[1] & 
[…]

### 2024-04-07 Main Paper/paper.qmd
editing the final paper

@@
 ---
-title: "How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18?"
+title: "How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?"
 author: 
@@
 
+```{R}
+#| include: false
+#| warning: false
+#| message: false
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+
+# Import the dataset from a CSV file
+df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/dataverse_files/social_media_mental_health.csv")
+
+set.seed(123)  # Set seed for reproducibility
+data <- df %>% sample_n(100)
+```
+
 # Table of Contents
@@
   - Research Gap and Objectives
+
 - Data
+
 - Results
@@
   - Correlation Analysis between Social Media Usage and Mental Health Indicators
-  - Subgroup Analysis by Age, Gender, and Socioeconomic Status
+  - Subgroup Analysis by Age
+
 - Discussion
@@
   - Suggestions for Future Research
+
 - References
@@
 
-Social media platforms have become ubiquitous in the lives of adolescents, providing avenues for communication, self-expression, and social interaction.
-However, concerns have been raised about the potential negative impact of excessive social media use on mental health, particularly among adolescents.
-Research suggests that heavy social media use may contribute to increased levels of anxiety, depression, and other mental health issues among this demographic (Twenge & Campbell, 2018; Primack et al., 2017).
+Social media platforms have become an integral part of adolescents' lives, offering channels for communication, self-expression, and social interaction.
+However, concerns regarding the potential adverse effects of excessive social media use on mental health, particularly among adolescents, have garnered increasing attention.
+Research, including studies like that by Twenge [@Twenge2018], suggests a link between heavy social media use and heightened levels of anxiety, depression, and other mental health issues among this demographic.
 
@@
 
-Understanding the relationship between social media usage and adolescent mental health is crucial for several reasons.
-Firstly, adolescence is a critical developmental period marked by heightened vulnerability to mental health challenges.
-Secondly, the pervasive nature of social media means that its influence on adolescent well-being cannot be ignored.
-Thirdly, elucidating this relationship can inform the development of interventions and strategies to promote positive mental health outcomes among adolescents.
+Understanding the intricate relationship between social media usage and adolescent mental health is paramount for several reasons.
+Firstly, adolescence constitutes a critical developmental period characterized by heightened vulnerability to mental health challenges, as highlighted by Sawyer et al.
+[@Sawyer2018].
+Secondly, the pervasive nature of social media necessitates acknowledgment of its profound influence on adolescent well-being.
+Thirdly, unraveling this relationship holds promise for informing the development of interventions and strategies aimed at fostering positive mental health outcomes among adolescents, as underscored by Best et al.
+[@Best2014].
 
@@
 
-While numerous studies have examined the association between social media use and mental health outcomes among adolescents, there remains a need for further research to comprehensively understand this complex relationship.
-This study aims to address this gap by investigating the frequency and duration of social media usage and their correlation with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18.
+Although numerous studies have explored the association between social media use and mental health outcomes among adolescents, a significant research gap persists, demanding further investigation to comprehensively understand this multifaceted relationship.
+This study endeavors to bridge this gap by delving into the frequency and duration of social media usage and their correlation with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19.
+Through a nuanced exploration, this research seeks to contribute to the existing body of knowledge and offer insights that can inform targeted interventions and support mechanisms tailored to the unique needs of adolescents in the digital age.
+
+\newpage
 
@@
 
-The synthetic data is generated using Python with the pandas and numpy libraries. It creates a DataFrame to organize the data and exports it to a CSV file.
+The synthetic dataset was generated using Python 3.9.7 [@Python2022], leveraging the pandas (version 1.3.3)[@pandas2022] and numpy (version 1.21.2)[@Harris2020] libraries.
+A DataFrame structure from the pandas library was utilized to organize the data, which was then exported to a CSV file using pandas' `to_csv()` function.
 
-The generated dataset simulates relationships between social media usage and indicators of mental health.
-Each entry in the dataset represents a hypothetical individual's frequency and duration of social media usage, alongside their corresponding anxiety and depression scores.
-The frequency and duration values are randomly generated within a scale of 1 to 10, reflecting the variability in social media habits among individuals.
-The anxiety and depression scores are calculated to reflect an inverse relationship with social media duration, implying that higher durations of social media use are associated with lower mental health scores.
-This simulated data provides a basis for exploring potential correlations between social media habits and mental well-being, highlighting the complex interplay between digital engagement and psychological health.
+This dataset simulates the relationships between social media usage and indicators of mental health.
+Each entry represents a hypothetical individual's frequency and duration of social media usage, along with corresponding anxiety and depression scores.
+The frequency and duration values are randomly generated within a scale of 1 to 10, capturing the diversity in social media habits among individuals.
+Anxiety and depression scores are calculated to exhibit an inverse relationship with social media duration, suggesting that longer durations of social media use are associated with lower mental health scores.
+
+To visualize and explore potential correlations between social media habits and mental well-being, R 4.1.2 [@Rmanual] was employed.
+Specifically, ggplot2 (version 3.3.5)[@Wickham2016], a popular package in R for creating visualizations, was utilized to generate graphs and analyze the data further.
+This integration of Python for data generation and R for visualization provides a comprehensive approach to exploring the complex interplay between digital engagement and psychological health.
+
+We can see the summary of the data below:
+
+```{R}
+#| echo: false
+#| fig-cap: Estimated Coefficients
+summary(data)
+```
+
+\newpage
 
@@
 
-The results revealed varying patterns of social media usage among adolescents, with a significant proportion reporting frequent and prolonged engagement with social media platforms.
+The study unveiled diverse patterns of social media engagement among adolescents, showcasing a substantial portion reporting frequent and extended usage of social media platforms.
+Figure 1 provides a descriptive illustration of the distribution of social media usage frequency among adolescents, offering valuable insights into the prevalent usage trends within this demographic.
 
-[Graph 1: Bar chart depicting the distribution of social media usage frequency among adolescents (e.g., hours per day, days per week).]
+```{R}
+#| echo: false
+#| fig-cap: Bar chart depicting the distribution of social media usage frequency among adolescents
+# Graph 1: Bar chart depicting the distribution of social media usage frequency among adolescents
+graph1 <- ggplot(data, aes(x = Social_Media_Frequency)) +
+  geom_bar(fill = "skyblue", color = "black") +
+  labs(title = "Distribution of Social Media Usage Frequency",
+       x = "Social Media Usage Frequency",
+       y = "Count") +
+  theme_minimal()
+print(graph1)
+```
 
@@
 
-Correlation analysis indicated a statistically significant positive correlation between the frequency and duration of social media usage and levels of anxiety and depression among adolescents.
+Correlation analysis revealed a statistically significant positive correlation between the frequency and duration of social media usage and the levels of anxiety and depression among adolescents.
+Figure 2 depicts the correlation between the duration of social media usage and anxiety levels among adolescents, providing a visual representation of this noteworthy relationship.
 
-[Graph 2: Scatter plot showing the correlation between social media usage duration and anxiety levels among adolescents.]
+```{R}
+#| echo: false
+#| fig-cap: Scatter plot showing the correlation between social media usage duration and anxiety levels among adolescents
+# Graph 2: Scatter plot showing the correlation between social media usage duration and anxiety levels among adolescents
+graph2 <- ggplot(data, aes(x = Social_Media_Duration, y = Anxiety_Score)) +
+  geom_point(color = "blue") +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  labs(title = "Correlation between Social Media Usage Duration and Anxiety Levels",
+       x = "Social Media Usage Duration",
+       y = "Anxiety Score") +
+  theme_minimal()
+print(graph2)
+```
 
-## Subgroup Analysis by Age, Gender, and Socioeconomic Status
+## Subgroup Analysis by Age
 
-Subgroup analysis demonstrated that the relationship between social media usage and mental health outcomes differed based on demographic factors such as age, gender, and socioeconomic status.
+Subgroup analysis showcased that the association between social media usage and mental health outcomes varied depending on demographic factor such as age.
+Figure 3 visually portrays the divergence in social media usage duration across different age groups, shedding light on the nuanced relationship between social media engagement and age demographics.
 
-[Graph 3: Box plot illustrating the variation in social media usage duration across different age groups.]
+```{R}
+#| echo: false
+#| fig-cap: Box plot illustrating the variation in social media usage duration across different age groups
+# Graph 3: Box plot illustrating the variation in social media usage duration across different age groups
+graph3 <- ggplot(data, aes(x = factor(Age), y = Social_Media_Duration)) +
+  geom_boxplot(fill = "lightgreen", color = "black") +
+  labs(title = "Variation in Social Media Usage Duration Across Age Groups",
+       x = "Age Group",
+       y = "Social Media Usage Duration") +
+  theme_minimal()
+print(graph3)
+```
+
+\newpage
 
@@
 
-The findings suggest that excessive social media usage may be associated with adverse mental health outcomes among adolescents, highlighting the need for targeted interventions and preventive measures.
+Upon analyzing the results and findings, it becomes evident that excessive social media usage correlates with adverse mental health outcomes among adolescents, highlighting the imperative for targeted interventions and preventive measures.
+The data reveals a clear positive association between greater social media engagement and increased instances of mental health issues.
+Moreover, it underscores a trend where social media usage escalates with age.
 
-## Implications for Adolescent Mental Health Interventions
+Figure 1 presents a bar chart depicting the distribution of social media usage frequency among adolescents, showcasing how often they engage with various platforms.
+This visualization provides a clear picture of the prevalence and intensity of social media use within the studied population.
 
-The study underscores the importance of promoting healthy social media habits and digital literacy skills among adolescents to mitigate the potential negative impact on mental health.
-Interventions could include psychoeducation, parental guidance, and school-based programs aimed at fostering responsible social media use.
+Furthermore, Figure 2, a scatter plot, demonstrates the correlation between social media usage duration and anxiety levels among adolescents.
+This graphical representation elucidates the relationship between the two variables, emphasizing the potential impact of prolonged social media exposure on mental well-being.
+
+Additionally, Figure 3, a box plot, illustrates the variation in social media usage duration across different age groups.
+By visually comparing the distribution of usage duration among various age cohorts, this visualization aids in identifying any age-related patterns or trends in social media consumption habits.
+
+Consequently, the study emphasizes the critical importance of promoting healthy social media habits and fostering digital literacy skills among adolescents to mitigate potential negative impacts on mental health.
+Interventions such as psychoeducation, parental guidance, and school-based programs aimed at encouraging responsible social media use are strongly advocated.
+These interventions can be tailored to address specific age groups and usage patterns revealed by the presented figures, thus enhancing their effectiveness in safeguarding adolescent mental well-being in the digital age.
 
@@
 
-Limitations of the study include reliance on self-reported data, which may be subject to recall bias, as well as the cross-sectional design, which precludes establishing causality.
-Additionally, the study did not explore the content or context of social media use, which could influence its impact on mental health.
+The study is subject to several limitations, primarily stemming from its reliance on self-reported data and the cross-sectional design.
+Self-reported data introduces the potential for recall bias, as participants may inaccurately remember or misrepresent their social media usage habits or mental health status.
+This bias could skew the results, leading to an inaccurate portrayal of the association between social media usage and mental health outcomes.
+Furthermore, the cross-sectional design inhibits the establishment of causality, as it only captures a snapshot in time.
+Without longitudinal data, it's challenging to discern whether excessive social media use directly causes adverse mental health effects or if other factors contribute to this relationship.
+
+Moreover, the study's scope was limited by its failure to delve into the content or context of social media use.
+The nature of interactions, the types of content consumed or shared, and the social dynamics within online platforms can significantly influence the impact of social media on mental health.
+For example, exposure to cyberbullying, comparison with idealized representations, or excessive screen time before bedtime may exacerbate mental health issues.
+By overlooking these nuances, the study may not capture the full complexity of how social media affects adolescents' well-being.
+Addressing these limitations in future research could provide a more nuanced understanding of the relationship between social media usage and mental health outcomes among adolescents.
 
@@
 
-Future research should employ longitudinal designs to better elucidate the causal relationship between social media usage and mental health outcomes among adolescents.
-Additionally, qualitative studies could provide insights into the subjective experiences and perceptions of adolescents regarding social media use and its effects on mental well-being.
+Future research endeavors should focus on exploring the intricate interplay between social media usage and adolescents' gender and social status, discerning how these factors shape mental health outcomes.
+By dissecting these dynamics, researchers can uncover whether certain gender groups or social strata are more vulnerable to negative mental health effects from particular types of social media interactions or content consumption.
+This understanding can inform the development of tailored interventions and support systems, addressing the diverse needs of adolescents based on their unique identities and social contexts.
+
+Additionally, integrating real-time data collection methods, such as online forums and social media monitoring tools, can offer deeper insights into the complex relationship between social media use and mental well-being.
+These approaches provide a more authentic portrayal of adolescents' online behaviors and experiences, enabling researchers to track changes over time and understand the evolving impact of social media on mental health.
+Leveraging such methodologies can enhance our comprehension of the mechanisms underlying social media's influence on adolescents' well-being, facilitating the design of more effective interventions and policies to promote positive online experiences.
+
+\newpage
 

### 2024-04-08 Main Paper/paper.qmd
editing final

@@
 - Data
+  - Methodology
+  - Data Summary
 
@@
   - Suggestions for Future Research
+  - Conclusion
 
@@
 
-Social media platforms have become an integral part of adolescents' lives, offering channels for communication, self-expression, and social interaction.
-However, concerns regarding the potential adverse effects of excessive social media use on mental health, particularly among adolescents, have garnered increasing attention.
-Research, including studies like that by Twenge [@Twenge2018], suggests a link between heavy social media use and heightened levels of anxiety, depression, and other mental health issues among this demographic.
+Social media now plays a very important role in people's lives.
+It provides a forum for social contact, communication, and self-expression.
+We have seen that there's been a growing research on the possible negative impact of excessive social media use on mental health, especially among teenagers.
+Studies, such as the one conducted by Twenge [@Twenge2018], suggest a connection between high levels of social media use and a rise in mental health problems such as anxiety and depression in this group of people.
 
@@
 
-Understanding the intricate relationship between social media usage and adolescent mental health is paramount for several reasons.
-Firstly, adolescence constitutes a critical developmental period characterized by heightened vulnerability to mental health challenges, as highlighted by Sawyer et al.
-[@Sawyer2018].
-Secondly, the pervasive nature of social media necessitates acknowledgment of its profound influence on adolescent well-being.
-Thirdly, unraveling this relationship holds promise for informing the development of interventions and strategies aimed at fostering positive mental health outcomes among adolescents, as underscored by Best et al.
-[@Best2014].
+It is critical to understand the complex relationship that exists between teenage mental health and social media use for a alot of reasons.The following are a few important ones:
+
+  - First off, as Sawyer et al. [@Sawyer2018] point out, adolescence is a crucial developmental stage marked by increased susceptibility to  mental health issues.
+  - Secondly, social media's widespread use indicates that it has a significant impact on adolescent wellbeing.
+  - Third, as highlighted by Best et al.
+[@Best2014], dissecting this link has the potential to inform the creation of therapies and tactics meant to promote favorable mental health outcomes for teenagers.
 
@@
 Although numerous studies have explored the association between social media use and mental health outcomes among adolescents, a significant research gap persists, demanding further investigation to comprehensively understand this multifaceted relationship.
-This study endeavors to bridge this gap by delving into the frequency and duration of social media usage and their correlation with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19.
-Through a nuanced exploration, this research seeks to contribute to the existing body of knowledge and offer insights that can inform targeted interventions and support mechanisms tailored to the unique needs of adolescents in the digital age.
+By investigating the frequency and duration of social media usage among teenagers aged 13-19 and their link with mental health indicators including depression and anxiety, this study aims to close this gap.
+By means of a sophisticated investigation, this study aims to make a valuable contribution to the current corpus of information and provide discernments that can guide focused interventions and methods of support catered to the particular requirements of teenagers in the digital era.
 
@@
 # Data
+
+## Methodology
 
@@
 This integration of Python for data generation and R for visualization provides a comprehensive approach to exploring the complex interplay between digital engagement and psychological health.
+
+## Data Summary
 
@@
 Consequently, the study emphasizes the critical importance of promoting healthy social media habits and fostering digital literacy skills among adolescents to mitigate potential negative impacts on mental health.
-Interventions such as psychoeducation, parental guidance, and school-based programs aimed at encouraging responsible social media use are strongly advocated.
+Interventions such as psychological education, parental guidance, and school-based programs aimed at encouraging responsible social media use are strongly advocated.
 These interventions can be tailored to address specific age groups and usage patterns revealed by the presented figures, thus enhancing their effectiveness in safeguarding adolescent mental well-being in the digital age.
@@
 Self-reported data introduces the potential for recall bias, as participants may inaccurately remember or misrepresent their social media usage habits or mental health status.
-This bias could skew the results, leading to an inaccurate portrayal of the association between social media usage and mental health outcomes.
-Furthermore, the cross-sectional design inhibits the establishment of causality, as it only captures a snapshot in time.
+This bias may distort the findings and provide a false impression of the relationship between social media use and outcomes related to mental health.
+Moreover, because the cross-sectional design only records a single point in time, it makes it difficult to demonstrate causality.
 Without longitudinal data, it's challenging to discern whether excessive social media use directly causes adverse mental health effects or if other factors contribute to this relationship.
@@
 For example, exposure to cyberbullying, comparison with idealized representations, or excessive screen time before bedtime may exacerbate mental health issues.
-By overlooking these nuances, the study may not capture the full complexity of how social media affects adolescents' well-being.
-Addressing these limitations in future research could provide a more nuanced understanding of the relationship between social media usage and mental health outcomes among adolescents.
+The study might not fully understand the intricacy of how social media influences the wellbeing of adolescents if these subtleties are ignored.
+Future studies that address these constraints may yield a more detailed picture of the connection between teenage social media use and mental health outcomes.
 
@@
 These approaches provide a more authentic portrayal of adolescents' online behaviors and experiences, enabling researchers to track changes over time and understand the evolving impact of social media on mental health.
-Leveraging such methodologies can enhance our comprehension of the mechanisms underlying social media's influence on adolescents' well-being, facilitating the design of more effective interventions and policies to promote positive online experiences.
+By utilizing these approaches, we may improve our understanding of the mechanisms that underlie the impact of social media on the wellbeing of adolescents.
+This will make it easier to create policies and interventions that will encourage pleasant experiences on the internet.
+
+## Conclusion
+
+The study's conclusions highlight the urgent need for preventative actions to address the negative effects of excessive social media use on teenage mental health.
+We have learned a great deal about the relationship between teenage use of social media and poor mental health outcomes thanks to the perceptive data analysis and trend display.
+
+The study emphasizes the value of encouraging digital literacy and positive social media behaviors, but it also recognizes some of its shortcomings, mainly with regard to the cross-sectional design and dependence on self-reported data.
+These restrictions make it necessary to interpret the results with caution and highlight the significance of further studies that aim to explore the intricacies of the connection between social media use and mental health.
+
+In the future, it will be crucial to create focused interventions and support networks that cater to the various requirements of teenagers according to their gender, socioeconomic standing, and online habits.
+We can build a deeper understanding of this complicated phenomenon and provide teenagers the tools they need to navigate the digital ecosystem in a healthier and more resilient way by embracing cutting-edge research approaches and examining the intricate interactions between social media use and mental health.
+In the end, we can try to create a more secure and encouraging online environment for the welfare of future generations by cooperating across disciplines and industries.
 

### 2024-04-09 Main Paper/paper.qmd
paper done

@@
 df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/dataverse_files/social_media_mental_health.csv")
+# Change th efile location to wherever your file is located.
 
@@
   - Interpretation of Findings
-  - Implications for Adolescent Mental Health Interventions
+  - What can be done?
   - Limitations of the Study
@@
 - References
-
-\newpage
 
@@
 
-  - First off, as Sawyer et al. [@Sawyer2018] point out, adolescence is a crucial developmental stage marked by increased susceptibility to  mental health issues.
-  - Secondly, social media's widespread use indicates that it has a significant impact on adolescent wellbeing.
-  - Third, as highlighted by Best et al.
-[@Best2014], dissecting this link has the potential to inform the creation of therapies and tactics meant to promote favorable mental health outcomes for teenagers.
+  - As Sawyer et al. [@Sawyer2018] points out, adolescence is a crucial developmental stage marked by increased susceptibility to  mental health issues.
+  - Impact on self-esteem: Social media platforms often present curated, idealized versions of people's lives, which can lead to feelings of inadequacy or low self-esteem among teenagers who compare themselves to these unrealistic standards.
+  - As highlighted by Best et al. [@Best2014], dissecting this link has the potential to inform the creation of therapies and tactics meant to promote favorable mental health outcomes for teenagers.
+  - Sleep disturbances: Excessive use of social media, particularly before bedtime, can disrupt teenagers' sleep patterns, leading to fatigue, irritability, and difficulty concentrating, which can negatively impact their mental health and overall well-being.
+  - Comparison culture: Social media fosters a culture of comparison, where teenagers constantly compare their lives, appearance, and achievements to those of their peers, often leading to feelings of inadequacy, envy, and depression.
 
@@
 By means of a sophisticated investigation, this study aims to make a valuable contribution to the current corpus of information and provide discernments that can guide focused interventions and methods of support catered to the particular requirements of teenagers in the digital era.
-
-\newpage
 
@@
 ```
-
-\newpage
 
@@
 
-\newpage
-
 # Discussion
@@
 These interventions can be tailored to address specific age groups and usage patterns revealed by the presented figures, thus enhancing their effectiveness in safeguarding adolescent mental well-being in the digital age.
+
+## What can be done?
+
+Based on the analysis and findings found, several targeted interventions and preventive measures can be implemented to address the adverse effects of excessive social media usage on adolescent mental health:
+
+  - Psychological Education: Develop educational programs aimed at increasing adolescents' awareness of the potential risks associated with excessive social media use, such as cyberbullying, negative self-comparison, and sleep disturbances.
+Provide resources and strategies for coping with these challenges effectively.
+
+  - Parental Guidance: Offer guidance and support to parents on how to monitor and regulate their children's social media usage effectively.
+Encourage open communication between parents and adolescents about social media habits and their impact on mental health.
+
+  - School-Based Programs: Implement school-based interventions focused on promoting responsible social media use and digital literacy skills.
+Incorporate topics such as online etiquette, critical thinking, and media literacy into the curriculum to empower adolescents to navigate the digital landscape safely.
+
+  - Promotion of Offline Activities: Encourage adolescents to participate in offline activities and hobbies that promote social interaction, physical exercise, and mental well-being as alternatives to excessive social media use.
+Provide opportunities for offline socialization and engagement within communities.
+
+  - Regulation and Policy Development: Advocate for policies and regulations that promote responsible social media practices and protect adolescents from harmful content and online harassment.
+Collaborate with social media platforms, policymakers, and stakeholders to establish guidelines for age-appropriate usage and content moderation.
+
+  - Research and Monitoring: Continuously monitor trends in social media usage and its impact on adolescent mental health through ongoing research and data collection.
+Use findings to inform the development of targeted interventions and policy recommendations that address emerging challenges in the digital landscape.
+
+By implementing these interventions in a comprehensive and collaborative manner, stakeholders can work together to promote healthy social media habits and safeguard the mental well-being of adolescents in the digital age.
 

### 2024-04-09 Main Paper/paper.qmd
fianl edit

@@
   - Raghav Kanda
-thanks: "Code and data are available at: "
+thanks: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
 date: April 10, 2024
@@
 bibliography: refer.bib
+footer: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
 ---

### 2024-04-17 Main Paper/paper.qmd
added the modela and solved some errors

--- 2024-04-09 Main Paper/paper.qmd
@@
   - Raghav Kanda
-thanks: "Code and data are available at: "
+thanks: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
 date: April 10, 2024
 date-format: long
-abstract: ""
+abstract: "This paper investigates the correlation between the frequency and duration of social media usage and indicators of mental health, such as anxiety and depression, among adolescents aged 13-19.
+Drawing upon a synthetic dataset and employing a sophisticated analytical approach, the study explores the relationship between social media habits and mental well-being.
+Findings reveal significant positive correlations between heightened social media engagement and increased levels of anxiety and depression among adolescents.
+Moreover, subgroup analysis highlights age-related variations in social media usage patterns and their association with mental health outcomes.
+The study underscores the critical importance of promoting healthy social media behaviors and fostering digital literacy skills among adolescents to mitigate potential negative impacts on mental health.
+Additionally, it identifies key areas for future research and intervention, emphasizing the need for tailored approaches that address the diverse needs of teenagers in the digital age."
 format: pdf
@@
 df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/dataverse_files/social_media_mental_health.csv")
-# Change th efile location to wherever your file is located.
+# Change the file location to wherever your file is located.
 
@@
 - Data
-  - Methodology
+  - Model
+  - Methodology and Cleaning
   - Data Summary
@@
 
-## Methodology
+## Model
 
-The synthetic dataset was generated using Python 3.9.7 [@Python2022], leveraging the pandas (version 1.3.3)[@pandas2022] and numpy (version 1.21.2)[@Harris2020] libraries.
-A DataFrame structure from the pandas library was utilized to organize the data, which was then exported to a CSV file using pandas' `to_csv()` function.
+The linear regression model employed in this script seeks to predict anxiety scores in adolescents based on their age, social media usage frequency, and duration of engagement on social media platforms [@Rmanual].
+Following the conventional linear regression equation, Anxiety_Score = B0 + B1 * Age + B2 * Social_Media_Frequency + B3 * Social_Media_Duration + E, where B0 represents the intercept and B1, B2, and B3 denote the coefficients associated with each independent variable, while E denotes the error term (Fox & Weisberg, 2019).
+It is posited that with increasing age and higher levels of social media activity, adolescents may experience elevated anxiety levels, corroborating findings from previous research on the relationship between excessive social media use and mental health issues among young individuals
+
+## Methodology and Cleaning
+
+The synthetic dataset was generated using Linear regression m odel in the model.r file.
+This R script generates synthetic data to simulate the relationship between social media usage and indicators of mental health among adolescents aged 13-18.
+It begins by loading the necessary libraries, including `dplyr` for data manipulation.
+Then, it defines a sample size of 3000 and sets a seed for reproducibility.
+Random data is generated for the age of the teens, social media usage frequency, and duration, with the frequency and duration increasing as age increases to mimic real-world trends.
+Anxiety and depression scores are calculated based on the social media usage and duration, assuming higher levels of usage correlate with increased mental health problems.
+The data is organized into a dataframe and exported to a CSV file.
+Finally, a linear regression model is fitted to predict anxiety scores using age, social media frequency, and duration as predictors.
+The summary of the model, including coefficient estimates and significance levels, is printed to assess the relationship between social media usage and anxiety scores.
+
+We used R [@Rmanual] for data cleaning and processing, utilizing packages like tidyverse [@tidy] for data manipulation.
+Other packages used includes `ggplot2` [@ggplot], `dplyr` [@dp], `readr` [@read], `tibble` [@tib], `knitr` [@knit], `ggbeeswarm` [@gg], `ggrepel` [@repel], `kableExtra`[@kable], `readxl`[@readxl], `MASS`[@mass], `rstanarm`[@rstan], `modelsummary`[@model].
 
@@
 Specifically, ggplot2 (version 3.3.5)[@Wickham2016], a popular package in R for creating visualizations, was utilized to generate graphs and analyze the data further.
-This integration of Python for data generation and R for visualization provides a comprehensive approach to exploring the complex interplay between digital engagement and psychological health.
+This integration of linear regression for data generation and R for visualization provides a comprehensive approach to exploring the complex interplay between digital engagement and psychological health.
 

### 2024-04-17 dataverse_files/data.r

@@ -38,6 +38,6 @@ graph3 <- ggplot(data, aes(x = factor(Age), y = Social_Media_Duration)) +
   theme_minimal()
 
 # Display the graphs
-print(graph1)
+# print(graph1)
 print(graph2)
-print(graph3)
+# print(graph3)

### 2024-04-17 dataverse_files/dataset.py

@@ -1,33 +1,0 @@
-import pandas as pd
-import numpy as np
-
-# Define sample size
-sample_size = 3000
-
-# Generate random data for age of the teen (between 13 and 18)
-age = np.random.randint(13, 19, sample_size)
-
-# Generate random data for social media usage frequency and duration
-# Increase social media usage as age increases
-social_media_frequency = np.random.randint(age * 0.5, age * 1.5 + 1, sample_size)
-social_media_duration = np.random.randint(np.maximum(age * 0.5, 1), np.minimum(age * 1.5 + 1, 25), sample_size)  # Ensure max duration is 24 hours
-
-# Generate random data for indicators of mental health (anxiety and depression)
-# Increase mental health problems as social media use increases
-anxiety_scores = (100 - np.random.randint(0, 101, sample_size)) * social_media_duration / 10
-depression_scores = (100 - np.random.randint(0, 101, sample_size)) * social_media_duration / 10
-
-# Create a DataFrame to hold the data
-data = pd.DataFrame({
-    'Age': age,
-    'Social_Media_Frequency': social_media_frequency,
-    'Social_Media_Duration': social_media_duration,
-    'Anxiety_Score': anxiety_scores,
-    'Depression_Score': depression_scores
-})
-
-# Export the DataFrame to a CSV file
-data.to_csv('dataverse_files/social_media_mental_health.csv', index=False)
-
-# Display the first few rows of the dataset
-print(data.head())

### 2024-04-17 dataverse_files/model.r

@@ -1,0 +1,42 @@
+# Load required library
+library(dplyr)
+
+# Define sample size
+sample_size <- 3000
+
+# Set seed for reproducibility
+set.seed(123)
+
+# Generate random data for age of the teen (between 13 and 18)
+age <- sample(13:18, sample_size, replace=TRUE)
+
+# Generate random data for social media usage frequency and duration
+# Increase social media usage as age increases
+social_media_frequency <- sample(age * 0.5:(age * 1.5 + 1), sample_size, replace=TRUE)
+social_media_duration <- sample(pmax(age * 0.5, 1):(pmin(age * 1.5 + 1, 25)), sample_size, replace=TRUE)  # Ensure max duration is 24 hours
+
+# Generate random data for indicators of mental health (anxiety and depression)
+# Increase mental health problems as social media use increases
+anxiety_scores <- (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10
+depression_scores <- (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10
+
+# Create a data frame to hold the data
+data <- data.frame(
+  Age = age,
+  Social_Media_Frequency = social_media_frequency,
+  Social_Media_Duration = social_media_duration,
+  Anxiety_Score = anxiety_scores,
+  Depression_Score = depression_scores
+)
+
+# Export the data frame to a CSV file
+write.csv(data, "dataverse_files/social_media_mental_health.csv", row.names = FALSE)
+
+# Display the first few rows of the dataset
+print(head(data))
+
+# Fit a linear regression model to predict anxiety scores
+model <- lm(Anxiety_Score ~ Age + Social_Media_Frequency + Social_Media_Duration, data=data)
+
+# Print the summary of the model
+print(summary(model))

### 2024-04-17 paper/paper.qmd
edited the structure of the files and the contents of some

--- 2024-04-17 Main Paper/paper.qmd
@@
   - Raghav Kanda
-thanks: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
-date: April 10, 2024
+thanks: "[Code and Data available Here](https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health)"
+date: 10 April 2024
 date-format: long
@@
 bibliography: refer.bib
-footer: "Code and data are available at: https://github.com/o8RaV/How-does-the-frequency-and-duration-of-social-media-usage-correlate-with-indicators-of-mental-health"
 ---
@@
 # Import the dataset from a CSV file
-df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/dataverse_files/social_media_mental_health.csv")
+df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/data/social_media_mental_health.csv")
 # Change the file location to wherever your file is located.

### 2024-04-17 scripts/data.r

@@ -4,7 +4,7 @@ library(dplyr)
 library(tidyr)
 
 # Import the dataset from a CSV file
-df <- read.csv("dataverse_files/social_media_mental_health.csv")
+df <- read.csv("data/social_media_mental_health.csv")
 
 set.seed(123)  # Set seed for reproducibility
 data <- df %>% sample_n(100)
@@ -38,6 +38,6 @@ graph3 <- ggplot(data, aes(x = factor(Age), y = Social_Media_Duration)) +
   theme_minimal()
 
 # Display the graphs
-# print(graph1)
+print(graph1)
 print(graph2)
-# print(graph3)
+print(graph3)

### 2024-04-17 scripts/model.r

@@ -30,7 +30,7 @@ data <- data.frame(
 )
 
 # Export the data frame to a CSV file
-write.csv(data, "dataverse_files/social_media_mental_health.csv", row.names = FALSE)
+write.csv(data, "data/social_media_mental_health.csv", row.names = FALSE)
 
 # Display the first few rows of the dataset
 print(head(data))
@@ -40,3 +40,4 @@ model <- lm(Anxiety_Score ~ Age + Social_Media_Frequency + Social_Media_Duration
 
 # Print the summary of the model
 print(summary(model))
+saveRDS(model, "data/linear_regression_model.rds")

### 2024-04-17 output/paper/paper.qmd
making the structure better

--- 2024-04-17 paper/paper.qmd
@@
 # Import the dataset from a CSV file
-df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/data/social_media_mental_health.csv")
+df <- read.csv("C:/Users/ragha/Desktop/How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-18/input/data/social_media_mental_health.csv")
 # Change the file location to wherever your file is located.

### 2024-04-17 input/scripts/data.r

@@ -4,7 +4,7 @@ library(dplyr)
 library(tidyr)
 
 # Import the dataset from a CSV file
-df <- read.csv("data/social_media_mental_health.csv")
+df <- read.csv("input/data/social_media_mental_health.csv")
 
 set.seed(123)  # Set seed for reproducibility
 data <- df %>% sample_n(100)

### 2024-04-17 input/scripts/model.r

@@ -30,7 +30,7 @@ data <- data.frame(
 )
 
 # Export the data frame to a CSV file
-write.csv(data, "data/social_media_mental_health.csv", row.names = FALSE)
+write.csv(data, "input/data/social_media_mental_health.csv", row.names = FALSE)
 
 # Display the first few rows of the dataset
 print(head(data))
@@ -40,4 +40,4 @@ model <- lm(Anxiety_Score ~ Age + Social_Media_Frequency + Social_Media_Duration
 
 # Print the summary of the model
 print(summary(model))
-saveRDS(model, "data/linear_regression_model.rds")
+saveRDS(model, "input/data/linear_regression_model.rds")

### 2024-04-17 output/paper/paper.qmd
made more relevant graphs and readings

@@
 Figure 2 depicts the correlation between the duration of social media usage and anxiety levels among adolescents, providing a visual representation of this noteworthy relationship.
+Figure 3 depicts the correlation between the duration of social media usage and depression levels among adolescents, providing a visual representation of this noteworthy relationship.
 
@@
 
+```{R}
+#| echo: false
+#| fig-cap: Scatter plot showing the correlation between social media usage duration and depression levels among adolescents
+# Graph 2_1: Scatter plot showing the correlation between social media usage duration and depression levels among adolescents
+graph2_1 <- ggplot(data, aes(x = Social_Media_Duration, y = Depression_Score)) +
+  geom_point(color = "green") +
+  geom_smooth(method = "lm", se = FALSE, color = "black") +
+  labs(title = "Correlation between Social Media Usage Duration and Depression Levels",
+       x = "Social Media Usage Duration per day",
+       y = "Depression Score(out of 100)") +
+  theme_minimal()
+print(graph2_1)
+```
+
 ## Subgroup Analysis by Age
@@
 Subgroup analysis showcased that the association between social media usage and mental health outcomes varied depending on demographic factor such as age.
-Figure 3 visually portrays the divergence in social media usage duration across different age groups, shedding light on the nuanced relationship between social media engagement and age demographics.
+Figure 4 visually portrays the divergence in social media usage duration across different age groups, shedding light on the nuanced relationship between social media engagement and age demographics.
 
@@
 
-Furthermore, Figure 2, a scatter plot, demonstrates the correlation between social media usage duration and anxiety levels among adolescents.
+Furthermore, Figure 2 and Figure 3, scatter plots, demonstrates the correlation between social media usage duration and anxiety and depression levels among adolescents.
 This graphical representation elucidates the relationship between the two variables, emphasizing the potential impact of prolonged social media exposure on mental well-being.
 
-Additionally, Figure 3, a box plot, illustrates the variation in social media usage duration across different age groups.
+Additionally, Figure 4, a box plot, illustrates the variation in social media usage duration across different age groups.
 By visually comparing the distribution of usage duration among various age cohorts, this visualization aids in identifying any age-related patterns or trends in social media consumption habits.

### 2024-04-17 input/scripts/data.r

@@ -25,8 +25,17 @@ graph2 <- ggplot(data, aes(x = Social_Media_Duration, y = Anxiety_Score)) +
   geom_point(color = "blue") +
   geom_smooth(method = "lm", se = FALSE, color = "red") +
   labs(title = "Correlation between Social Media Usage Duration and Anxiety Levels",
-       x = "Social Media Usage Duration",
-       y = "Anxiety Score") +
+       x = "Social Media Usage Duration per day",
+       y = "Anxiety Score(out of 100)") +
+  theme_minimal()
+
+# Graph 2_1: Scatter plot showing the correlation between social media usage duration and depression levels among adolescents
+graph2_1 <- ggplot(data, aes(x = Social_Media_Duration, y = Depression_Score)) +
+  geom_point(color = "green") +
+  geom_smooth(method = "lm", se = FALSE, color = "black") +
+  labs(title = "Correlation between Social Media Usage Duration and Depression Levels",
+       x = "Social Media Usage Duration per day",
+       y = "Depression Score(out of 100)") +
   theme_minimal()
 
 # Graph 3: Box plot illustrating the variation in social media usage duration across different age groups
@@ -34,10 +43,11 @@ graph3 <- ggplot(data, aes(x = factor(Age), y = Social_Media_Duration)) +
   geom_boxplot(fill = "lightgreen", color = "black") +
   labs(title = "Variation in Social Media Usage Duration Across Age Groups",
        x = "Age Group",
-       y = "Social Media Usage Duration") +
+       y = "Social Media Usage Duration per day") +
   theme_minimal()
 
 # Display the graphs
-print(graph1)
-print(graph2)
-print(graph3)
+# print(graph1)
+# print(graph2)
+print(graph2_1)
+# print(graph3)

### 2024-04-17 input/scripts/model.r

@@ -12,13 +12,13 @@ age <- sample(13:18, sample_size, replace=TRUE)
 
 # Generate random data for social media usage frequency and duration
 # Increase social media usage as age increases
-social_media_frequency <- sample(age * 0.5:(age * 1.5 + 1), sample_size, replace=TRUE)
+social_media_frequency <- sample(1:(age * 2), sample_size, replace=TRUE)  # Number of times person opens social media
 social_media_duration <- sample(pmax(age * 0.5, 1):(pmin(age * 1.5 + 1, 25)), sample_size, replace=TRUE)  # Ensure max duration is 24 hours
 
 # Generate random data for indicators of mental health (anxiety and depression)
 # Increase mental health problems as social media use increases
-anxiety_scores <- (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10
-depression_scores <- (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10
+anxiety_scores <- pmin(100, (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10)
+depression_scores <- pmin(100, (100 - sample(0:100, sample_size, replace=TRUE)) * social_media_duration / 10)
 
 # Create a data frame to hold the data
 data <- data.frame(
